---
title: "Groupme Data Analysis"
output: html_notebook
---

This is an data project to the evolution of our social space in VFA.

Questions?
- Who contributes the most?
- Meme frequency by time of day?
- Themes of the most liked posts?
- Who gets @'d the most?
- Who @'s the most
- Who gives their likes most freely?

Let's get our data:
```{r}
#Dear computer:
setwd("~/Documents/Coding/Data")
library(readr)
data = as.data.frame(read_csv("groupme_cleaned_72918.csv"))
View(data)
class(data)
```

```{r}
#libraies
library(lattice)
library(boot)
library(MASS)
install.packages("ggplot2")
library(ggplot2)
install.packages("anytime")
library(anytime)
```

Data cleaning and prep:
```{r}
#****************DATA CLEANING*****************************

data$created_at<-anytime(data$created_at)
colnames(data)[colnames(data)=="created_at"] <- "time_sent"

data$attachments<-as.character(data$attachments)
data$favorited_by<-as.character(data$favorited_by)

######## ADD LIKES COLUMN ##########
# The string to search in
s <-data$favorited_by[which(data$favorited_by!="[]")]
# The character to search for
p <- ","
# Replace all occurrences by the empty string - note that gsub uses regular expressions, so escape p accordingly
s2 <- gsub(p,"",s) # Count the length difference
data$likes<-rep(0,nrow(data))
data$likes[which(data$favorited_by!="[]")] <- nchar(s) - nchar(s2) + 1 # numOcc now contains the number of occurrences of p in s

####### ADD attachment columns COLUMN
data$pic_attch <- grepl("image",data$attachments)
data$mention_attch <- grepl("mentions",data$attachments)

####### FIND NUMBER MENTIONS
data$mention_ids <- rep(0,nrow(data))
data$mention_ids<-sapply(strsplit(data$attachments,"'user_ids': [",fixed="TRUE"),'[',2)
data$mention_ids<-sapply(strsplit(data$mention_ids,"]}",fixed="TRUE"),'[',1)

# The string to search in
s <-data$mention_ids[which(!is.na(data$mention_ids))]
# The character to search for
p <- ","
# Replace all occurrences by the empty string - note that gsub uses regular expressions, so escape p accordingly
s2 <- gsub(p,"",s) # Count the length difference
data$mention_count<-rep(0,nrow(data))
data$mention_count[which(!is.na(data$mention_ids))] <- nchar(s) - nchar(s2) + 1
```

Write the data to a csv
```{r}
write.csv(data, file = "GroupmeDataXXXXXX.csv")
View(data)
nrow(data)
```

Get text mining packages:
```{r}
install.packages("tm")
install.packages("SnowballC")
install.packages("wordcloud")
install.packages("RColorBrewer")
install.packages("RCurl")
install.packages("XML")
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(RCurl)
library(XML)
```

Define rquery.wordcloud
```{r}
#++++++++++++++++++++++++++++++++++
# rquery.wordcloud() : Word cloud generator
# - http://www.sthda.com
#+++++++++++++++++++++++++++++++++++
# x : character string (plain text, web url, txt file path)
# type : specify whether x is a plain text, a web page url or a file path
# lang : the language of the text
# excludeWords : a vector of words to exclude from the text
# textStemming : reduces words to their root form
# colorPalette : the name of color palette taken from RColorBrewer package, 
  # or a color name, or a color code
# min.freq : words with frequency below min.freq will not be plotted
# max.words : Maximum number of words to be plotted. least frequent terms dropped
# value returned by the function : a list(tdm, freqTable)
rquery.wordcloud <- function(x, type=c("text", "url", "file"), 
                          lang="english", excludeWords=NULL, 
                          textStemming=FALSE,  colorPalette="Dark2",
                          min.freq=3, max.words=200)
{ 
  library("tm")
  library("SnowballC")
  library("wordcloud")
  library("RColorBrewer") 
  
  if(type[1]=="file") text <- readLines(x)
  else if(type[1]=="url") text <- html_to_text(x)
  else if(type[1]=="text") text <- x
  
  # Load the text as a corpus
  docs <- Corpus(VectorSource(text))
  # Convert the text to lower case
  docs <- tm_map(docs, content_transformer(tolower))
  # Remove numbers
  docs <- tm_map(docs, removeNumbers)
  # Remove stopwords for the language 
  docs <- tm_map(docs, removeWords, stopwords(lang))
  # Remove punctuations
  docs <- tm_map(docs, removePunctuation)
  # Eliminate extra white spaces
  docs <- tm_map(docs, stripWhitespace)
  # Remove your own stopwords
  if(!is.null(excludeWords)) 
    docs <- tm_map(docs, removeWords, excludeWords) 
  # Text stemming
  if(textStemming) docs <- tm_map(docs, stemDocument)
  # Create term-document matrix
  tdm <- TermDocumentMatrix(docs)
  m <- as.matrix(tdm)
  v <- sort(rowSums(m),decreasing=TRUE)
  d <- data.frame(word = names(v),freq=v)
  # check the color palette name 
  if(!colorPalette %in% rownames(brewer.pal.info)) colors = colorPalette
  else colors = brewer.pal(8, colorPalette) 
  # Plot the word cloud
  set.seed(1234)
  wordcloud(d$word,d$freq, min.freq=min.freq, max.words=max.words,
            random.order=FALSE, rot.per=0.35, 
            use.r.layout=FALSE, colors=colors)
  
  invisible(list(tdm=tdm, freqTable = d))
}

#++++++++++++++++++++++
# Helper function
#++++++++++++++++++++++
# Download and parse webpage
html_to_text<-function(url){
  library(RCurl)
  library(XML)
  # download html
  html.doc <- getURL(url)  
  #convert to plain text
  doc = htmlParse(html.doc, asText=TRUE)
 # "//text()" returns all text outside of HTML tags.
 # We also don’t want text such as style and script codes
  text <- xpathSApply(doc, "//text()[not(ancestor::script)][not(ancestor::style)][not(ancestor::noscript)][not(ancestor::form)]", xmlValue)
  # Format text vector into one character string
  return(paste(text, collapse = " "))
}
```

Most Common Words Overall:          
```{r}
rquery.wordcloud(data$text, type=c("text"), 
        lang="english", excludeWords = c("s","d","y","m","ve","'","",",","ll",",","`","re"), 
        textStemming = FALSE, colorPalette="Dark2",
        max.words=200)
```

Common Words in Top 200 Most Likes (Top 5%) Messages:
```{r}
library(plyr) 
top200 = head(arrange(data,desc(likes)), n = 200) #get 200 most liked comments
View(top200$text) #view

rquery.wordcloud(top200$text, type=c("text"), 
        lang="english", excludeWords = c("s","d","y","m","ve","'","",",","ll",",","`","re"), 
        textStemming = FALSE, colorPalette="Dark2",
        max.words=200)


```

Correlation between post activity and total likes accumulated:



